Untitled

### 2023-01-25 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
up to fw

---
title: "Untitled"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}

@@

checklist_df <- data.frame(Ref = c(paste0("T",1:6),
                                        paste0("I",1:4),
                                        paste0("M",1:2),
                                        paste0("E",1:3),
                                        paste0("L",1:3),
                                        paste0("Y",1:2)),
                           Standard = c("Publicly archived",
                                        "Documented",
                                        "Consistent syntax",
                                        "Literately programmed",

@@

                                        "Reproducible",

@@

                                        "Deprecation",
                                        "Separate code and data",
                                        "Encapsulated",
                                        "Inheriting",
                                        "Copyleft code",
                                        "Liberal, safe data terms",
                                        "Citation tools",
                                        "User interface"),

@@

@@

@@

                                        "No"),
                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",

@@

@@

                                           "Retired code is deprecated using lifecycle package tools (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )",
                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulated  modules. Examples are the items beginning with Scorz, Specific and Youthvars that are listed in this table: https://ready4-dev.github.io/ready4/articles/V_01.html#current-ready4-framework-modules as well as the S4 classess from the TTU package listed here: https://ready4-dev.github.io/TTU/reference/index.html ",
                                           "All code libraries include functions. The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above).",
                                           "All modules (see item M2) inherit from the Ready4Module class and can be inherited from.",
                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures. It was created to demonstrate generalised applications of study algorithms.",
                                           "No Shiny app user interface has yet been developed."))

>>>>

---
title: "Untitled"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---

```{r checktb, tab.cap='Framework checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}

@@

checklist_df <- data.frame(Ref = c(paste0("A",1:7),#paste0("T",1:6),paste0("I",1:4),paste0("M",1:2),paste0("E",1:3),paste0("L",1:3), paste0("Y",1:2)
                                   paste0("R",1:9),
                                   paste0("U",1:4)),
                           Standard = c("Public",
                                        "Documentation",
                                        "Syntax",
                                        "Literate programming",

@@

                                        "Reproducibility",
                                        "Citation tools",#
                                        # Reuse
                                        "Code licenses",
                                        "Data terms",
                                        "Separation",
                                        "Encapsulated, inheriting",
                                        "Functions",
                                        "User interface",
                                        ## Updatable

@@

                                        "Deprecation"
                                       ),

@@

                                        # Reuse
                                        "Yes", # "Yes",

@@

                                        ## Updatable

@@

                                        "Yes"
                                        ),
                           Description = c("Development and archived code for 5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are available. See https://www.ready4-dev.com/docs/getting-started/software/libraries/types/module/ (for libraries), https://www.ready4-dev.com/docs/getting-started/software/executables/programs/ (for programs) and https://www.ready4-dev.com/docs/getting-started/software/executables/subroutines/",

@@

                                           # Reuse
                                           "Four [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155] out of five libraries include encapsulating and inheriting modules. See: https://www.ready4-dev.com/docs/model/finding-modules/ ", 
                                           "All code libraries include functions. The most complete list of functions for each library is available by clicking the 'Manual - Developer (PDF)' link on each package's documentation homepage (see item T2 above)",
                                           "All module data-structures and algorithms are distributed as code libraries",
                                            "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures. It was created to demonstrate generalised applications of study algorithms.",                                           #
                                           "No Shiny app user interface has yet been developed.",
                                        ## Updatable

@@

                                           "Retired code is deprecated using lifecycle package tools (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"
                                          ))
